The language of generalization: Probability, vagueness, and interaction

### 2018-03-24 paper/comgen-paper.Rmd
add table of habituals items to appendix
address comments in case 2

Understanding the language of generalization is a project with far-reaching implications.
The language of generalization is ubiquitous in everyday conversation and conveys rich meanings, impacting motivation [@Cimpian2007], transmitting stereotyped beliefs about social categories [@Rhodes2012], making meaning from experience [@Orvell2017].
It is highly-prevalent in child-directed speech [@Gelman2008] and its ability to refer to abstractions beyond the present context suggests its centrality to the growth of conceptual knowledge [@Gelman2004].
Finally, it is believed every language can express generalization [@Behrens2005; @Carlson1995].

@@

@@

>>>>

Understanding the language of generalization is a project with far-reaching implications.
The language of generalization is ubiquitous in everyday conversation and conveys rich meanings, impacting motivation [@Cimpian2007], transmitting stereotyped beliefs about social categories [@Rhodes2012], and making meaning from experience [@Orvell2017].
It is highly-prevalent in child-directed speech [@Gelman2008] and its ability to refer to abstractions beyond the present context suggests its centrality to the growth of conceptual knowledge [@Gelman2004].
Finally, it is believed every language can express generalization [@Behrens2005; @Carlson1995].

@@

We note that regressions model that takes into account the referent prevalence and the distinctiveness of the feature do reasonable jobs at explaining some of the variance in the endorsement data.
This kind of model, however, is merely a re-description of the data and does not represent a bonafide theory of the semantics of a generalization. 
<!-- \ndg{this point is unclear. maybe save it for general discussion?} -->
A theory of the semantics of a generalization must formalize the conditions under which the generalization is true or false as well as how those truth-conditions relate to endorsement. 
That is precisely what our information-theoretic model does.

@@

```{r child = 'appendix-habitualsItems.Rmd'}
```
